Introduction to Lattices Attacks\\``Cryptography''

### 2021-06-03 paper.tex
Determinant definition

To introduce the mathematics of lattices a basic linear algebra background is needed, so the second chapter is a summary of the
basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
explain them, but we also tried to gives some geometrically intuition behind some operations.

@@

>>>>

To introduce the mathematics of lattices a basic linear algebra background is needed, so the second chapter is a summary of the
basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
explain them, but we also tried to gives some geometrical intuition behind some operations.

@@

\begin{definition}
    \textbf{Determinant}
\end{definition}

The \textit{determinant} of a square matrix is a function that satisfies the following properties:

\begin{enumerate}
    \item The determinant is linear in each row.
    \item The determinant reverses sign if two rows are interchanged.
    \item The determinant of the identity matrix is equal to 1.
\end{enumerate}

If the determinant of a matrix is $0$ then the matrix is called \textbf{singular} (without an inverse).\\

Grant Sanderson created fantastic animations to understand the geometrical intuition behind the \textit{determinant}\cite{determinant}.
